Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-20 optim.qmd
update intro

Significant efforts have been devoted to enhancing the functionality of
PP and facilitating a better experience in the visualisation process.
@cook1995grand introduced the PP guided tour, which enabled interactive
visualisation of the optimisation to visually explore high-dimensional
data. It is implemented in the R [@R] package `tourr`[@tourr].
@RJ-2021-105 highlighted potential problems of the optimisation routine
implemented. While improving the quality of the optimisation solutions
in the tour is essential, it is also important to be able to watch the
projected data as the optimisation progresses. Therefore, it is of
interest to integrate the guided tour with a global optimisation
algorithm and examine the characteristics and advantages of such
implementation.

The artificial Jellyfish Search Optimiser (JSO) [@chou_novel_2021] is a
swarm-based metaheuristic optimisation algorithm inspired by the search
behaviour of jellyfish in the ocean. It is one of the latest swarm
intelligence algorithms [@rajwar_exhaustive_2023], which was shown to
have stronger search ability and faster convergence with fewer
parameters compared to classic optimisation methods
[@chou_novel_2021]-[@chou_recent_2022].

>>>>

Significant efforts have been devoted to enhancing the functionality of
PP and facilitating a better experience in the visualisation process.
@cook1995grand introduced the PP guided tour, which enabled interactive
visualisation of the optimisation to visually explore high-dimensional
data. It is implemented in the R [@R] package `tourr`[@tourr].
@RJ-2021-105 highlighted potential problems of the optimisation routine
implemented. While improving the quality of the optimisation solutions
in the tour is essential, it is also important to be able to watch the
projected data as the optimisation progresses. As such, it is pertinent to integrate the guided tour with a global optimisation
algorithm that is efficient in finding the global optimal and enables viewing of the projected data during the exploration process.

The artificial Jellyfish Search Optimiser (JSO) [@chou_novel_2021] is a swarm-based metaheuristic designed to solve global optimisation problems.
Inspired by the search behaviour of jellyfish in the ocean, JSO is one of the latest swarm intelligence algorithms [@rajwar_exhaustive_2023], which was shown to have stronger search ability and faster convergence with fewer parameters compared to classic optimisation methods [@chou_novel_2021]-[@chou_recent_2022]. These practical properties makes JSO a strong candidate in integration with the PP guided tour. As such, it is of interest to explore the potential of JSO in enhancing the PP guided tour and examine the characteristics and advantages of such implementation.

### 2024-06-20 optim.tex
update intro

\begin{keyword}
    projection pursuit \sep Jellyfish Search Optimiser (JSO) \sep 
    Optimisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners, frame hidden, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Significant efforts have been devoted to enhancing the functionality of
PP and facilitating a better experience in the visualisation process.
\citet{cook1995grand} introduced the PP guided tour, which enabled
interactive visualisation of the optimisation to visually explore
high-dimensional data. It is implemented in the R \citep{R} package
\texttt{tourr}\citep{tourr}. \citet{RJ-2021-105} highlighted potential
problems of the optimisation routine implemented. While improving the
quality of the optimisation solutions in the tour is essential, it is
also important to be able to watch the projected data as the
optimisation progresses. Therefore, it is of interest to integrate the
guided tour with a global optimisation algorithm and examine the
characteristics and advantages of such implementation.

The artificial Jellyfish Search Optimiser (JSO) \citep{chou_novel_2021}
is a swarm-based metaheuristic optimisation algorithm inspired by the
search behaviour of jellyfish in the ocean. It is one of the latest
swarm intelligence algorithms \citep{rajwar_exhaustive_2023}, which was
shown to have stronger search ability and faster convergence with fewer
parameters compared to classic optimisation methods
\citep{chou_novel_2021}-\citep{chou_recent_2022}.

@@

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, leftrule=.75mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, colback=white, arc=.35mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toptitle=1mm, opacityback=0, bottomtitle=1mm, breakable, rightrule=.15mm, bottomrule=.15mm, titlerule=0mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, coltitle=black]

>>>>

\begin{keyword}
    projection pursuit \sep Jellyfish Search Optimiser (JSO) \sep 
    Optimisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, frame hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

Significant efforts have been devoted to enhancing the functionality of
PP and facilitating a better experience in the visualisation process.
\citet{cook1995grand} introduced the PP guided tour, which enabled
interactive visualisation of the optimisation to visually explore
high-dimensional data. It is implemented in the R \citep{R} package
\texttt{tourr}\citep{tourr}. \citet{RJ-2021-105} highlighted potential
problems of the optimisation routine implemented. While improving the
quality of the optimisation solutions in the tour is essential, it is
also important to be able to watch the projected data as the
optimisation progresses. As such, it is pertinent to integrate the
guided tour with a global optimisation algorithm that is efficient in
finding the global optimal and enables viewing of the projected data
during the exploration process.

The artificial Jellyfish Search Optimiser (JSO) \citep{chou_novel_2021}
is a swarm-based metaheuristic designed to solve global optimisation
problems. Inspired by the search behaviour of jellyfish in the ocean,
JSO is one of the latest swarm intelligence algorithms
\citep{rajwar_exhaustive_2023}, which was shown to have stronger search
ability and faster convergence with fewer parameters compared to classic
optimisation methods \citep{chou_novel_2021}-\citep{chou_recent_2022}.
These practical properties makes JSO a strong candidate in integration
with the PP guided tour. As such, it is of interest to explore the
potential of JSO in enhancing the PP guided tour and examine the
characteristics and advantages of such implementation.

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toptitle=1mm, breakable, colbacktitle=quarto-callout-note-color!10!white, leftrule=.75mm, left=2mm, titlerule=0mm, colframe=quarto-callout-note-color-frame, coltitle=black, opacitybacktitle=0.6, colback=white, toprule=.15mm, bottomtitle=1mm, arc=.35mm, bottomrule=.15mm, opacityback=0]
